% !TeX program = pdflatex
% Geoff Boeing's Curriculum Vitae
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\RequirePackage[l2tabu,orthodox]{nag} % warn if using any obsolete commands
\documentclass[11pt,letterpaper]{report} % document style

% load encoding and font packages for pdflatex, in order
\usepackage[T1]{fontenc}    % output 8-bit encoded fonts
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage{ebgaramond}     % document's serif font
\usepackage{helvet}        % document's sans serif font

% load babel, csquotes, and microtype in order
\usepackage[USenglish]{babel} % auto-regionalize hyphens, quote marks, etc
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[babel=true]{microtype} % enable micro-typographic adjustments

% load everything else
\usepackage{datetime} % enable formatting of date output
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{geometry} % manually set page margins
\usepackage{setspace} % custom line spacing
\usepackage{tabto}    % make nice tabbing
\usepackage{titlesec} % allow custom section fonts

% load hyperref last for compatibility
\usepackage{hyperref} % enable hyperlinks and pdf metadata

% what is your name?
\newcommand{\myname}{Umit Aslan}

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% for slightly indented and small text
\newcommand{\indentedsmall}[1]{\hspace{2pt}\small{#1}\normalsize}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase heading font tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        Ph.D.\ Candidate in Learning Sciences \\
        School of Education and Social Policy \\
        Northwestern University
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \raggedleft{}
        +1 (224) 307--3550 \\
        \href{mailto:umitaslan@u.northwestern.edu}{umitaslan@u.northwestern.edu} \\
        \href{https://umitaslan.com}{umitaslan.com}
    \end{minipage}


    % ------------------------
    % ----- EDUCATION -----
    % ------------------------


    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab{}Learning Sciences, Northwestern University, Evanston, IL, {\small Dec.} 2025  {\footnotesize (anticipated)} \\

        \vspace{4pt}

        {\small Dissertation Title: \enquote{Reimagining research methods in an age of complexity: studying people’s reasoning of complex systems through agent-based-construction [abc] interviews}} \\

        \vspace{4pt}

        {\small Committee: Uri Wilensky (Chair), Sharona Levy, Bruce Sherin} \\

        \vspace{8pt}

        \item[M.S.]  \tab{}Science and Mathematics Education, Bogazici University, Istanbul, Turkiye, 2014 \\

        \vspace{4pt}

        {\small Thesis Title: \enquote{Fostering students' learning of probability through video game programming}} \\

        \vspace{4pt}

        {\small Committee: Yavuz Akpinar (Chair), Gulseren Karagoz Akar, Tufan Adiguzel}

        \vspace{8pt}

        \item[B.S.]  \tab{}Educational Technologies, Bogazici University, Istanbul, Turkiye, 2010

    \end{tablist}


    % ------------------------
    % ----- PUBLICATIONS -----
    % ------------------------

    \section*{Publications}

    \subsection*{Journal Articles}

    \begin{tablist}

        \item[2024] \tab{}\textbf{Aslan, U}., Horn, M., \& Wilensky, U. (2024). Why are some students \enquote{not into} computational thinking activities embedded within high school science units? Key takeaways from a microethnographic discourse analysis study. \textit{Science Education}, 108, 929--956. \href{https://doi.org/10.1002/sce.21850}{doi:10.1002/sce.21850}

        \item[2015] \tab{}Akpinar, Y. \& \textbf{Aslan, U}. (2015). Supporting children's learning of probability through video game programming. \textit{Journal of Educational Computing Research}, 53(2), 228--259. \href{https://doi.org/10.1177/0735633115598492}{doi:10.1177/0735633115598492}

    \end{tablist}



    \subsection*{Book Chapters}

    \begin{tablist}

        \item[2017] \tab{}\textbf{Aslan, U}., Dabholkar, S., \& Wilensky, U. (2017). Developing multi-agent-based thought experiments: A case study on the evolution of gamete dimorphism. In G. Sukthankar. \& J. A. Rodriguez-Aguilar (Eds.), \textit{Autonomous Agents and Multiagent Systems: AAMAS 2017 Workshops, Best Papers}, (pp. 51--65). Springer, Verlag. \href{https://doi.org/10.1007/978-3-319-71682-4\_4}{doi:10.1007/978-3-319-71682-4\_4}

    \end{tablist}

    \subsection*{Journal Articles (in preparation)}

    \begin{tablist}

        \item[] \tab{}\textbf{Aslan, U}., Levy, S., LaGrassa, N., Davey, B., Horn, M., \& Wilensky, U. (in preparation). Connected Chemistry redux: Outcomes of a design experiment on reconstructing the CC1 unit through the CT-STEM lens.

        \item[] \tab{}\textbf{Aslan, U}., Dabholkar, S., Woods, P., Noel, I., \& Wilensky, U. (in preparation). Reconstructing population-level evolutionary theories through spatially explicit multi-agent-based modeling: A case study on the evolution of anisogamy.

    \end{tablist}

    \subsection*{Conference Papers (peer reviewed)}

    \begin{tablist}

        \item[2021] \tab{}\textbf{Aslan, U}., Wu, S. P., Horn, M., \& Wilensky, U. (2021). Connecting the \enquote{chemistry triplet} through co-designing computational models with teachers: A case study on calorimetry. Paper presented at \textit{American Educational Research Association (AERA) 2021 Annual Meeting}. Meeting Held Virtually. \href{https://doi.org/10.3102/1686353}{doi:10.3102/1686353}

        \item[2020] \tab{}\textbf{Aslan, U}., LaGrassa, N., Horn, M., \& Wilensky, U. (2020). Phenomenological programming: A novel approach to designing domain-specific programming environments for science learning. In \textit{Proceedings of the Interaction Design and Children Conference (IDC) 2020}, 299--310. Virtual Meeting. \href{https://doi.org/10.1145/3392063.3394428}{doi:10.1145/3392063.3394428}

        \item[] \tab{}\textbf{Aslan, U}., LaGrassa, N., Horn, M., \& Wilensky, U. (2020). Putting the taxonomy into practice: Investigating students’ learning of chemistry with integrated computational thinking activities. Paper accepted to \textit{American Educational Research Association (AERA) 2020 Annual Meeting}. \href{https://doi.org/10.3102/1584908}{doi:10.3102/1584908}

        \item[] \tab{}Kelter, J. Z., Peel, A., Bain, C., Dabholkar, S., \textbf{Aslan, U}., Horn, M., \& Wilensky, U. (2020). Seeds of (r)evolution: Constructionist co-design with high school science teachers. In \textit{Proceedings of the Constructionism Conference 2020}, 497--505.

        \item[] \tab{}\textbf{Aslan, U}., LaGrassa, N., Horn, M., \& Wilensky, U. (2020). Code-first learning environments for science education: a design experiment on kinetic molecular theory. In \textit{Proceedings of the Constructionism Conference 2020}, 206--219.

        \item[2019] \tab{}\textbf{Aslan, U}., Anton, G., Horn, M., \& Wilensky, U. (2019). Bringing powerful ideas to middle school students' lives through agent-based modeling. Paper presented at \textit{American Educational Research Association (AERA) 2019 Annual Meeting}. Toronto, ON. \href{https://doi.org/10.3102/1444571}{doi:10.3102/1444571}

        \item[2018] \tab{}\textbf{Aslan, U}. \& Wilensky, U. (2018). Agent-based Construction (a-b-c) interviews: A generative case study. In \textit{Proceedings of the Constructionism Conference 2018}, 125--137. Vilnius, Lithuania.

        \item[2017] \tab{}\textbf{Aslan, U}., Dabholkar, S., \& Wilensky, U. (2017). Developing multi-agent-based thought experiments: A case study on the evolution of gamete dimorphism. In \textit{Proceedings of the Multi-Agent-Based Simulation Workshop XVIII, MABS 2017}, 47--61. Sao Paolo, Brazil. \href{https://doi.org/10.1007/978-3-319-91587-6\_4}{doi:10.1007/978-3-319-91587-6\_4}

        \item[2016] \tab{}\textbf{Aslan, U}. \& Wilensky, U. (2016). Restructuration in practice: Challenging a pop-culture evolutionary theory through agent-based modeling. In \textit{Proceedings of the Constructionism Conference 2016}, 125--137. Bangkok, Thailand.


    \end{tablist}

    \subsection*{Conference Presentations (abstract reviewed)}

    \begin{tablist}

        \item[2021] \tab{}\textbf{Aslan, U}. \& Wilensky, U. (2021). Constructing the NetLogo Anisogamy model. Paper Presented at the \textit{First International Workshop on Agentization: Rendering Conventional Models with Agent-Based Computing}. Virtual meeting organized by George Mason University.

        \item[2016] \tab{}\textbf{Aslan, U}. \& Wilensky, U. (2016). Old tricks revisited: Studying probabilistic reasoning through incorporating computer modeling into Piagetian research. Paper Presented at the \textit{46th Annual Meeting of the Jean Piaget Society}. Chicago, IL.

        \item[2012] \tab{}\textbf{Aslan, U}.. (2012). Fostering students' learning of mathematics through creative computing. Paper Presented at the \textit{Scratch@MIT Conference}. Cambridge, MA.

    \end{tablist}


    % ------------------------
    % -- OTHER PUBLICATIONS --
    % ------------------------

    \subsection*{Other Publications}

    \begin{tablist}

        \item[2021] \tab{}\textbf{Aslan, U}. \& Wilensky, U. (2021). Beginner’s Interactive NetLogo Dictionary (BIND). Center for Connected Learning and Computer-Based Modeling, Northwestern University. Evanston, IL. \href{https://ccl.northwestern.edu/netlogo/bind/}{ccl.northwestern.edu/netlogo/bind/}

        \item[2020]     \tab{}Namowicz, C., Levites, L., \textbf{Aslan, U}., Lee, J., L., Horn, M., \& Wilensky, U. (2020). Energy in Chemical Reactions (open-source curricular unit). CT-STEM Research Project, Northwestern University. Evanston, IL. \href{https://ct-stem.northwestern.edu/curriculum/preview/1678/}{https://ct-stem.northwestern.edu/curriculum/preview/1678/}.

        \item[]     \tab{}Namowicz, C., Lindeman, K., \textbf{Aslan, U}., Lee, J., L., Horn, M., \& Wilensky, U. (2020). Kinetic Molecular Theory (open-source curricular unit). CT-STEM Research Project, Northwestern University. Evanston, IL. \href{https://ct-stem.northwestern.edu/curriculum/preview/2620/}{https://ct-stem.northwestern.edu/curriculum/preview/2620/}.

        \item[]     \tab{}\textbf{Aslan, U}., Namowicz, C., Levites, L., Horn, M., \& Wilensky, U. (2020). NetLogo Calorimetry Model (open-source computational model). Center for Connected Learning and Computer-Based Modeling, Northwestern University. Evanston, IL. \href{https://ccl.northwestern.edu/netlogo/models/Calorimetry}{https://ccl.northwestern.edu/netlogo/models/Calorimetry}.

        \item[2019] \tab{}\textbf{Aslan, U}., LaGrassa, N., Horn, M., \& Wilensky, U. (2019). Ideal Gas Laws - Connected Chemistry 2019 (open-source curricular unit). CT-STEM Research Project, Northwestern University. Evanston, IL. \href{https://ct-stem.northwestern.edu/curriculum/preview/565/}{https://ct-stem.northwestern.edu/curriculum/preview/565/}.

         \item[2016]     \tab{}\textbf{Aslan, U}. \& Wilensky, U. (2016). NetLogo Anisogamy Model (open-source computational model). Center for Connected Learning and Computer-Based Modeling, Northwestern University. Evanston, IL. \href{https://ccl.northwestern.edu/netlogo/models/Anisogamy}{https://ccl.northwestern.edu/netlogo/models/Anisogamy}.

    \end{tablist}


    % ------------------------
    % - RESEARCH EXPERIENCE --
    % ------------------------


    \section*{Research Experience}

    \subsection*{Northwestern University, Evanston, Illinois}

    \begin{tablist}

        \item[2020--25] \tab{}Ph.D. Dissertation in Learning Sciences (Supervisor: Uri Wilensky) \\

        \vspace{4pt}

        \indentedsmall{Designed and conducted a study on people's intuitive reasoning about complex systems}  \\
        \indentedsmall{Created a computationally-mediated research interview methodology}  \\
        \indentedsmall{Developed a computational knowledge analysis tool using NLP and network analysis} \\
        \indentedsmall{Published two peer-reviewed conference papers} \\

        \vspace{6pt}

        \item[2016--22] \tab{}Graduate Researcher, CT-STEM Research Project (Co-PIs: Uri Wilensky \& Michael Horn) \\

        \vspace{4pt}

        \indentedsmall{Developed novice-friendly programming activities for STEM courses} \\
        \indentedsmall{Co-designed CT-ified curricular units in-service teachers} \\
        \indentedsmall{Investigated students' learning of science and CT} \\
        \indentedsmall{Published one journal article and five peer-reviewed conference papers}

    \end{tablist}

    \subsection*{Bogazici University, Istanbul, Turkiye}

    \begin{tablist}

        \item[2012--14] \tab{}Master's Thesis in Science and Mathematics Education (Supervisor: Yavuz Akpinar) \\

        \vspace{4pt}

        \indentedsmall{Designed a middle-school unit for teaching probability through game programming activities} \\
        \indentedsmall{Conducted a quasi-experimental study on the effectiveness of the unit with 5th and 6th grade students} \\
        \indentedsmall{Published a journal article}

        \vspace{6pt}

        \item[2012--14] \tab{}Graduate Researcher, English as a Lingua Franca Project (Co-PIs: Yasemin Bayyurt \& Nikos Sifakis) \\

        \vspace{4pt}

        \indentedsmall{Established an LMS platform for a year-long in-service teacher PD program} \\
        \indentedsmall{Collected qualitative data on teachers' PD participation through the LMS}

        \vspace{6pt}

        \item[2012--14] \tab{}Graduate Researcher, Teaching ESL through Mobile Multimedia Project (PI: Gulcan Ercetin) \\

        \vspace{4pt}

        \indentedsmall{Developed an Android phone application to deliver multimedia ESL assessments} \\

        \vspace{6pt}

        \item[2010--12] \tab{}Graduate Researcher, Using Eye Tracking in ESL Research Project (PI: Gulcan Ercetin) \\

        \vspace{4pt}

        \indentedsmall{Collected eye-tracking data on ESL students' text reading strategies} \\
        \indentedsmall{Conducted quantitative analyses of eye-tracking data} \\

    \end{tablist}


    % ------------------------
    % ------ MENTORING -------
    % ------------------------


    \section*{Mentoring}

    \subsection*{Knowledge Analysis with NLP Project}

    \begin{itemize}
        \item Claire Schwartz, undergraduate research assistant, 2024--25
        \item Philip Dawny Philip, master's level research assistant, 2024--25
    \end{itemize}

    \subsection*{Beginner's Interactive NetLogo Dictionary (BIND)}

    \begin{itemize}
        \item James Hovet, undergraduate research assistant, 2021
        \item Nala Bishop, undergraduate research assistant, 2021
        \item Sydney Crawford, undergraduate research assistant, 2021
    \end{itemize}

    \subsection*{CT-STEM Research Project}

    \begin{itemize}
        \item Jamie Lee, undergraduate research assistant, 2019--21
        \item Mitchell Estberg, undergraduate research assistant, 2017--18
    \end{itemize}


    %------------------------
    % ----- TEACHING -----
    %------------------------


    \section*{Teaching Experience}

    \subsection*{Northwestern University, Evanston, Illinois}

    \begin{tablist}

        \item[2021] \tab{}Graduate Teaching Assistant, Advanced Qualitative Methods (Instructor: James Spillane)

        \item[2021] \tab{}Graduate Teaching Assistant, Mapping and Spatial Analysis (Instructor: David Uttal)

        \item[2017--19] \tab{}Graduate Teaching Assistant, Design of Technological Tools for Thinking and Learning (Instructor: Uri Wilensky)

    \end{tablist}

    \subsection*{Center for Talent Development, Evanston, Illinois}

    \begin{tablist}

        \item[2025] \tab{}Instructor, Brain and Behavior, CTD Summer Camp for Gifted Students (Grades 6--8)

        \item[2018] \tab{}Instructor, Using Technology to Solve Society's Tough Problems, CTD Weekend Enrichment Program for Gifted Students (Grades 6--8)

        \item[2016] \tab{}Instructor, Modeling Social and Natural Worlds With NetLogo, CTD Weekend Enrichment Program for Gifted Students (Grades 6--8)

    \end{tablist}

    \subsection*{Istanbul Topkapi University, Istanbul, Turkiye}

    \begin{tablist}

        \item[2013] \tab{}Adjunct Instructor, Web Design and Development

        \item[2011-2013] \tab{}Adjunct Instructor, Introduction to Mathematics for Creative Professionals

    \end{tablist}


    % ------------------------
    % ----- SERVICE -----
    % ------------------------

    \section*{Peer Review}

    \subsection*{Academic Journal Peer Reviewer}

    \begin{itemize}

        \item ACM Transactions on Computer-Human Interaction
        \item Journal of Educational Computing Research
        \item Journal of Research in Science Teaching
        \item Journal of Science Education and Technology
        \item Science Education
        \item Studies in Science Education

    \end{itemize}


    \subsection*{Conference Peer Reviewer}

    \begin{itemize}

        \item ACM Conference on Interaction Design and Children (IDC)
        \item ACM Conference on Human Factors in Computer Systems (CHI)
        \item Annual Meeting of the American Educational Research Association (AERA)%, 2019--2024
        \item Annual International Conference of the National Association for Research in Science Teaching (NARST)

    \end{itemize}



    \section*{Memberships}

    \begin{itemize}

        \item Association for Computing Machinery (ACM)
        \item American Educational Research Association (AERA)
        \item American Psychological Association (APA)
        \item International Society of the Learning Sciences (ISLS)
        \item National Association for Research in Science Teaching (NARST)

    \end{itemize}


    \section*{Grants}

    \begin{tablist}

        \item[2020] \tab{}Research Grant, Office of Undergraduate Research, Northwestern University, \$3,500.00 USD
        \item[2013] \tab{}Innovation Grant, Scientific and Technological Research Council of Turkey, \$121,000.00 USD
        \item[2011--12] \tab{}Teacher PD Grant, Google Computer Science for High School (CS4HS) Initiative, \$10,000.00 USD

    \end{tablist}



    \section*{Professional Employment}

    \begin{tablist}

        \item[2019--24] \tab{}Operations Manager, \textit{Roamers Therapy}, Chicago, IL
        \item[2016--22] \tab{}Graduate Research Assistant, \textit{Northwestern University}, Evanston, IL
        \item[2013--14] \tab{}Software Developer, \textit{Odyssey R\&D}, Istanbul, Turkiye
        \item[2011--13] \tab{}Software Developer \& Adjunct Instructor, \textit{Istanbul Topkapi University}, Istanbul, Turkiye
        \item[2010--11] \tab{}Software Developer, \textit{Istanbul Aydin University}, Istanbul, Turkiye

    \end{tablist}




    \section*{Spoken Languages}

    \begin{itemize}

        \item Turkish, Native Tongue
        \item English, Fluent
        \item Spanish, Conversational

    \end{itemize}


    % ------------------------
    % ------ REFERENCES ------
    % ------------------------


    \section*{References}

    \subsection*{Dr. Uri Wilensky}

    \begin{itemize}

        \item Northwestern University
        \item Professor of Learning Sciences, Computer Science, Cognitive Science, and Complex Systems
        \item Co-Chair,  Computer Science \& Learning Sciences Ph.D. Program
        \item Director, Center for Connected Learning and Computer-Based Modeling
        \item Email: \href{mailto: uri@northwestern.edu}{uri@northwestern.edu}
        \item Phone: (847) 467--7593
        \item Address: 2120 Campus Drive, Evanston, IL, 60208

        \end{itemize}


    \subsection*{Dr. Michael Horn}

    \begin{itemize}

        \item Northwestern University
        \item Professor of Learning Sciences and Computer Science
        \item Co-Chair,  Computer Science \& Learning Sciences Ph.D. Program
        \item Director, Tangible Interaction Design and Learning Laboratory
        \item Email: \href{mailto: michael-horn@northwestern.edu}{michael-horn@northwestern.edu}
        \item Phone: (617) 803--5501
        \item Address: 2120 Campus Drive, Evanston, IL, 60208

    \end{itemize}


    \subsection*{Dr. Sharona Levy}

    \begin{itemize}
        \item University of Haifa
        \item Professor of Learning, Instruction, and Teaching
        \item Head of Systems Learning \& Development Lab
        \item Email: \href{mailto: stlevy@edu.haifa.ac.il}{stlevy@edu.haifa.ac.il}
        \item Phone: (224) 307--3733
        \item Address: 199 Aba Khoushy Ave. Mount Carmel, Haifa, Israel 3498838
    \end{itemize}


    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        \monthyeardate\today
    \end{center}

\end{document}
